---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
Author: Raghu Bayya
---

## **Exercise with the data frame**

Let say you have a Bike Store near St. Catherine

Your store has 500 units of bikes with different size, color (green) and features.

In promotion on green environment (for Eco-friendly) you spend \$1.500.

The average price for single unit is \$650.99.

If customer, make purchase of more than \$8.650 will get a discount of 25% and 1 year service free

**ROI = ((Sales Growth-Marketing Cost) / Marketing Cost) \* 100%**

**Sales Growth Rate = ((Current Period Sales - Prior Period Sales) / Prior Period Sales) \* 100%**

```{r}
bike_sales <- read.csv('bike_clean.csv', header=T, na.strings='')
bike_sales
```

```{r}

```

```{r}
str(bike_sales)
```

```{r}

library(dplyr)
#bike_sales%>%filter(bike_sales$Purchased.Bike=="Yes")
New_bike<-bike_sales%>%mutate(Sales=bike_sales$Income*5/100)%>%filter(bike_sales$Purchased.Bike=="Yes")
print(New_bike)
```

```{r}
str(New_bike)
```

```{r}
actual_unit_sold <- 497 # Units sold with the promotion
Sales_price <- 650.99   # Price x single unit

print(actual_unit_sold)
print(Sales_price)
```

**Sales Revenue**

```{r}
Current_period_sales <- actual_unit_sold * Sales_price
print(paste("The Sales Revenue = ", Current_period_sales))
```

```{r}
#Previous_unit_sold <- sum(Sales$Purchased.Bike == "Yes")
#print(paste("Previous unit sold = ",Previous_unit_sold))
```

```{r}
Previous_Sales <- sum(New_bike$Sales)
print(paste("The Previous Sales = ", Previous_Sales))
```

**Sales Growth Rate+**

```{r}
Sales_Growth_Rate <- round(((Current_period_sales - Previous_Sales) / Previous_Sales)*100,2)
print(paste("Sales Growth Rate =", Sales_Growth_Rate,"%"))
```

**ROI**

```{r}
Marketing_Cost <- 1500
ROI <- round(((Current_period_sales - Previous_Sales) - Marketing_Cost) / Marketing_Cost,2)
print(paste("Previous Sales =", Previous_Sales))
print(paste("Actual Sales =", Current_period_sales))
print(paste("ROI =", ROI,"%"))
```

```{r}
#Sales1 <- Sales %>% filter(Marital.Status=="Married")
#Sales1
```

```{r}
#Sales2 <- Sales %>% filter(Marital.Status=="Single")
#Sales2
```
